Northern Andes plant species IUCN data

### 2023-03-02 code/L0/L0_Ecuador_plants_IUCN.Rmd
switch to reading in IUCN data downloaded from website that includes all plants

---
title: "Northern Andes plant species IUCN data"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "None"
data output: "NorthAndes_IUCN_plant_species.csv, NorthAndes_IUCN_plant_occ.csv, NorthAndes_IUCN_plant_habitat.csv"
project: "Frugivoria"
date: "2023-02-27"
output: html_document
---
# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
```

# Install and load required packages
```{r}
library(httr)
library(jsonlite)
library(rredlist)
library(dplyr)
library(mde)
library(DataExplorer)
library(summarytools)
```

# Set up token and api url
```{r}
## Token for accessing IUCN data through their API
## User must obtain a token (https://apiv3.iucnredlist.org/api/v3/token) before using the 'rredlist package'.
token <- 'f632af67ee5eef8446a8cb0ca394e1f1cb369ca5eab626edc4ea46e5698deb25'
api_url <- 'https://apiv3.iucnredlist.org/api/v3/'

@@

# North Andes species list
```{r}
#Ecuador
ecuador_species <- rl_sp_country("EC", key = token, parse = TRUE)
ecuador_species <- ecuador_species$result[1]
#Colombia
colombia_species <- rl_sp_country("CO", key = token, parse = TRUE)
colombia_species <- colombia_species$result[1]
#Venezuela
venezuela_species <- rl_sp_country("VE", key = token, parse = TRUE)
venezuela_species <- venezuela_species$result[1]

#combine all 3
northAndes_species <- rbind(ecuador_species, colombia_species, venezuela_species)
```

# Plant species list
```{r}
# Get codes for the different species groups
grp_codes <- GET(url = paste0(api_url, 'comp-group/list?token=', token))
code <-fromJSON(content(grp_codes, as = 'text'), simplifyDataFrame = TRUE, flatten = TRUE)$result
```

```{r}
# Get species list of all plants across all countries
mangrove_plants <- rl_comp_groups(group = 'mangrove_plants', key = token)
p1 <- as.data.frame(mangrove_plants$result)
seagrasses<- rl_comp_groups(group = 'seagrasses', key = token)
p2 <- as.data.frame(seagrasses$result)
cycads <- rl_comp_groups(group = 'cycads', key = token)
p3 <- as.data.frame(cycads$result)
magnolias <- rl_comp_groups(group = 'magnolias', key = token)
p4 <- as.data.frame(magnolias$result)
confiers <- rl_comp_groups(group = 'conifers', key = token)
p5 <- as.data.frame(confiers$result)
cacti <- rl_comp_groups(group = 'cacti', key = token)
p6 <- as.data.frame(cacti$result)

all_plants <- rbind(p1, p2, p3, p4, p5, p6)
```

# Generate Northern Andes plant species list
```{r}
northAndes_plants <- merge(all_plants, northAndes_species, by="taxonid")
```

# Get occurences for Northern Andes using species list
```{r}
get_occ <- function(ID) {
  rl_occ_country<- rl_occ_country(id=ID,key=token)$result
  if (class(rl_occ_country) == 'data.frame') {
    data.frame(taxonid=ID, rl_occ_country)
  } else {
    data.frame(taxonid=ID)
  }
}
northAndes_IUCN_plant_occ <- northAndes_plants %>%
  rowwise %>%
  do(get_occ(.$taxonid))
northAndes_IUCN_plant_occ <- as.data.frame(northAndes_IUCN_plant_occ)
```

# Get habitat for species list
```{r}
get_habitat <- function(ID) {
  habitat_by_sp<- rl_habitats(id=ID,key=token)$result
  if (class(habitat_by_sp) == 'data.frame') {
    data.frame(taxonid=ID, habitat_by_sp)
  } else {
    data.frame(taxonid=ID)
  }
}
northAndes_IUCN_plant_habitat <- northAndes_plants %>%
  rowwise %>%
  do(get_habitat(.$taxonid))
northAndes_IUCN_plant_habitat <- as.data.frame(northAndes_IUCN_plant_habitat)
```

>>>>

---
title: "Northern Andes plant species IUCN data"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "None"
data output: "NorthAndes_IUCN_plant_species.csv, NorthAndes_IUCN_plant_occ.csv"
project: "Frugivoria"
date: "2023-02-27"
output: html_document
---
# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
```

# Install and load required packages
```{r}
library(dplyr)
library(mde)
library(DataExplorer)
library(summarytools)
```

# Read in IUCN data
Data was obtained from https://www.iucnredlist.org/search?dl=true&permalink=bd0e6db7-6fb0-4ad3-ad6c-63da82cc0999
```{r}
assessments <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/assessments.csv"))
common_names <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/common_names.csv"))
conservation_needed <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/conservation_needed.csv"))
countries <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/countries.csv"))
credits <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/credits.csv"))
dois <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/dois.csv"))
fao <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/fao.csv"))
habitats <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/habitats.csv"))
plant_specific <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/plant_specific.csv"))
references <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/references.csv"))
research_needed <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/research_needed.csv"))
simple_summary <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/simple_summary.csv"))
synonyms <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/synonyms.csv"))
taxonomy <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/taxonomy.csv"))
threats <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/threats.csv"))
usetrade <- read.csv(file.path(data_path,"IUCN/Northern Andes 2 - Search Results/usetrade.csv"))
points_data <- read.csv(file.path(data_path,"IUCN/Northern Andes 3 - Range data Points/points_data.csv"))
```

the different tables joined using the "internalTaxonId" when viewing taxon information, or the "assessmentID" field to see assessment information, especially in cases where downloads include multiple assesments for a taxon (e.g. regional and global assessments).
```{r}

@@
